---
title: "Lab 6"
author: "Katie Pietrucha"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Example of a rank-based test

We'll make our own samples, using a psuedorandom generator.

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

Quick look histograms (built into R)

```{r}
hist(gp_1)

hist(gp_2)
```

Try a t-test:
```{r}
t.test(gp_1, gp_2)
```

What does p-value mean?

If bthese samples were drawn from populations with the same mean, then the probability of taking two random samples with means *at least as different* as the sample means we found by random chance (taking into account spread and sample size) is 19.8%.

Retain (fail to reject null hypothesis) the null hypothesis. >> There is no significant difference in means between group 1 and group 2.
(Don't say "accept" the null.)

Now let's comapre this outcome to a rank-based test.

## Mann Whitney U unpaired rank-based test

```{r}
mwu <- wilcox.test(gp_1, gp_2)

mwu
```

What does this p-value mean? 

If these samples were drawn from populations with the same ranks (medians), the probability of taking two random samples with ranks *at least this different* by chance is 0.28.

There is no significant difference in ranks (or medians) between group 1 and group 2 (statistical summary).

Example of writing it up: Median scores for group 1 (M = 14) and group 2 (M = 12) did not differ significantly. (Mann Whitney U test U(df) = 86, p = 0.28).

## Linear regression

Simple linear regression (single dependent bariable, a single independent variable)

```{r}
# Make an exploratory plot of penguin body mass vs. flipper length (X)
# When knitted, no part of code will show up in knitted document (include = FALSE command in r header)

ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point() +
  geom_smooth(method = "lm")

# Don't use geom_smooth in final document unless you can fully explain model and what it means, including the error bars
```

Find a linear regression model using ordinary least squares describing the relationship between flipper length and body mass for these penguins.

3 pieces:

- What type of model?
- What is the relationship to model (DV - IV(s))
- Where is the data that's used to create this model?

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)
```

### broom package returns model outputs as tidy data frames
```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm)

penguin_lm_tidy
```

How can I actually include my model equation in a report?

```{r}
extract_eq(model = penguin_lm, use_coefs = TRUE)
```

